### 2023-04-17 README.Rmd
update readme, remove HPC references
Update README.md/Rmd and faq.Rmd with correct instructions to start RStudio IDE in Apptainer/Singularity

### Using Apptainer/Singularity containers for HPC

@@

```bash
cd ~/rocker_test
sudo apptainer build container.sif container.def
apptainer instance start container.sif rangtest
```

@@

```bash
cd ~/rocker_test
sudo singularity build container.sif container.def
singularity exec container.sif R
```

Using the above example, `sessionInfo()` outputs the following. You have successfully gone back to the pre-pandemic time on your HPC.

@@

>>>>

### Using Apptainer/Singularity containers

@@

```bash
cd ~/rocker_test
apptainer build container.sif container.def
apptainer run container.sif R
```

@@

```bash
cd ~/rocker_test
sudo singularity build container.sif container.def
singularity run container.sif R
```

Using the above example, `sessionInfo()` outputs the following. You have successfully gone back to the pre-pandemic.

@@

### Apptainer/Singularity with RStudio IDE

For running RStudio IDE in Apptainer/Singulairty container, some writable folders and a config file have to be created locally:

```bash
mkdir -p run var-lib-rstudio-server
printf 'provider=sqlite\ndirectory=/var/lib/rstudio-server\n' > database.conf
```

After that, you can run the container:

```bash
apptainer exec \
    --env PASSWORD='set_your_password' \
    --bind run:/run,var-lib-rstudio-server:/var/lib/rstudio-server,database.conf:/etc/rstudio/database.conf \
    container.sif \
    /usr/lib/rstudio-server/bin/rserver \
    --auth-none=0 --auth-pam-helper-path=pam-helper \
    --server-user=$(whoami)
```

or

```bash
singularity exec \
    --env PASSWORD='set_your_password' \
    --bind run:/run,var-lib-rstudio-server:/var/lib/rstudio-server,database.conf:/etc/rstudio/database.conf \
    container.sif \
    /usr/lib/rstudio-server/bin/rserver \
    --auth-none=0 --auth-pam-helper-path=pam-helper \
    --server-user=$(whoami)
```

The default port is 8787, you can also change the port by adding `--www-port=` in the end of the line above (e.g. `--www-port=8080`).

Now open a browser and go to localhost:8787.
The default username is your local username, password as specified above (in this case `set_your_password`).
